PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-02-27 qfenv_paper/qf_environment.tex
Section 2 edited

\begin{abstract}
We examine the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
different density environments from $z=0.0-0.8$ using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
a stellar mass limited target galaxy population of 
$40430$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $106732$
galaxies from SDSS within redshift range $0.0375-0.145$. We classify  
these target galaxies as quiescent or star-forming using an evolving cut 
based on specific star formation rate (SSFR). For each of these galaxies 
we also measure its environment using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} constructed
from PRIMUS and SDSS. Based on its environment measurements we classify our target
population into high or low density environments.

With the target galaxy population divided into quiescent and star-forming galaxies 
in high and low density environments, we calculate the stellar mass functions 
(SMFs) for each of these subsamples. Over the redshift range $z=0.8$ to $0.0$, 
in high density environments we find that the SMFs of the quiescent galaxies 
increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ while the SMF 
of the star-forming galaxies evolves little for all masses. Meanwhile in low 
density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
galaxies evolves little for all stellar masses and the SMF of star-forming 
galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
Furthermore, we compute the $f_{\rm{Q}}$s using the SMFs in the subsamples to 
examine the evolution of the $f_{\rm{Q}}$ in high and low density environments
over the redshift range. We find that at $\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ 
increases by $\sim 0.15$ from $z=0.8$ to $0.0$ for both high and low environments. 
In addition, throughout the entire redshift range the difference between the
$f_{\rm{Q}}$ at high and low environment remains constant at $\sim 0.1$. 
These results suggest that the evolution of $f_{\rm{Q}}$ is independent of environment. 
\end{abstract}

%Section heading
\section{Introduction}
\begin{table*} %Subject to significant change based on the classification of environment
  \caption{Summary of Galaxy Subsample}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table*}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

\section{Sample Selection}
In this paper we are interested in measuring the evolution of the quiescent 
fraction over a wide range of redshifts and in different galaxy density environments. 
In order construct a sample with redshift depth and robust enough redshift values 
to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.

We begin with a brief summary of the PRIMUS data in Section \ref{sec:primus} followed by a summary of the SDSS data in Section \ref{sec:sdss}.
Then in Section \ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
We then obtain the environment for the target galaxy population using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we impose cuts on the target galaxy environment based on the edges of the survey.

@@

From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
in a simplified Bayesian framework.
\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A. of \cite{Moustakas:2013aa}.
The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
These generated model SEDs depend on population synthesis models and prior parameters.
In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.

@@

\subsection{Target Galaxy Samples} \label{sec:target} 
In this seciton we will define the target galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 0.8$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $log \mathcal{M}_{\rm{lim}} = log \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
and star-forming galaxies is included in the following section).
Finally, we use these polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
Note that these redshift bins will later be used to divide the target population during SMF and QF calculations.

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.06-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (\ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
We again refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We classify the galaxies from the target sample, defined in the last section, using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa}.
For a detailed description of the classification scheme, we refer readers to Section 3.2 in \cite{Moustakas:2013aa}.

To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
galaxies observed at least until $z \sim 2$.
As stated in \cite{Moustakas:2013aa}, the PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
determined by eye, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\label{eq:qsfclass} 
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation}
where $\mathcal{M}$ is the stellar mass of the galaxy.
If the target galaxy SFR and stellar mass place the galaxy above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
We use fixed cylindrical apertures with dimensions specified in Table \ref{tab:aperture} to probe the environment of the target sample galaxies. 
A fixed cylindrical apertures was chosen over a spherical one, often used in literature (e.g. \cite{Croton:2005aa}), due to redshift errors in the PRIMUS data 
and considerations of redshift space distortions within our PRIMUS data redshift range, $[0.2,1.0]$.
Furthermore, we use aperture dimensions listed in Table \ref{tab:aperture} based on the analysis of scale dependence for clustering in \cite{Blanton:2006aa}.
As \cite{Blanton:2006aa} suggests, galactic properties such as their star-formation histories are dependent on properties such as the masses of their host dark matter halos.
Hence, by employing fixed cylindrical apertures with $r_{\rm{ap}} = 1, 2 \rm{Mpc}$ we are able to probe the local small scale environment within the scales of the host dark matter halos.
As a comparison, we also include fixed cylindrical apertures with $r_{\rm{ap}} \ge 5 \rm{Mpc}$ to probe large scale environment, which \cite{Blanton:2006aa} finds to be unrelated to the 
recent star formation history of galaxies.

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first construct a volume limited {\it Environment Defining Population} (EDP) with absolute 
magnitude cut-offs ($M_{r}$) at each redshift bin. The $M_{r}$ cut-offs are selected so that  
the cumulative number density of all redshift bin are equal to one another. 
We use this fixed cumulative number density at each redshift bin in order to build an EDP with galaxies that 
have similar populations in all of the redshift bins i.e. accounts for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
In addition we use the highest redshift bin cumulative number density as the fixed number density 
%%%FINISH THIS SENTENCE
Furthermore \cite{Behroozi:2013aa}
\begin{figure*}
  \begin{center}
    \leavevmode
     \label{fig:smf}
     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}
    \end{center}
\end{figure*}

The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-0.8$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude limits ($M_{r,\rm{lim}}$) such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

>>>>

\begin{abstract}
We present the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
different density environments from $z=0.0$ to $0.8$ using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
a stellar mass limited galaxy population of 
$\sim 40000$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $\sim 100000$
galaxies from SDSS within redshift range $0.0375-0.145$. Using an evolving cut based on
specific star formation, we classify the galaxies as quiescent or star-forming and
measure its environment using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} we construct 
from PRIMUS and SDSS. Based on its environment we classify our target
population into dense or sparse environments.

With the target galaxy population divided into quiescent and star-forming galaxies 
in dense and sparse environments, we calculate the stellar mass functions 
(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
$z=0.8$ to $0.0$ for both high and low environments. 
In addition, throughout the redshift range the difference between the
$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
is independent of environment. 
%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
%galaxies evolves little for all stellar masses and the SMF of star-forming 
%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
\end{abstract}

%Section heading
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

\section{Sample Selection}
In this paper we are interested in measuring the evolution of the quiescent 
fraction over a wide range of redshifts and in different galaxy environments. 
In order construct a sample with redshift depth and robust enough redshift values 
to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.

We begin with a brief summary of the PRIMUS data in Section \ref{sec:primus} followed by a summary of the SDSS data in Section \ref{sec:sdss}.
Then in Section \ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
For each galaxy we obtain the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct the galaxy sample and its environment measurements for the edge effects of the surveys.

@@

From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
in a simplified Bayesian framework.
\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A. of \cite{Moustakas:2013aa}.
The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
These generated model SEDs depend on population synthesis models and prior parameters.
In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.
\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Density        &Quiescent  &Star-forming  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table}

@@

\subsection{Target Galaxy Samples} \label{sec:target} 
In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 0.8$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
and star-forming galaxies is included in the following section).
Finally, we use the polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
These redshift bins will later be used to divide the target sample in order to compute the SMFs and QFs.

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.0375-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (Section \ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
The absolute magnitude ($M_{r}$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
For further details we refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
galaxies observed at least until $z \sim 2$.
The PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\label{eq:qsfclass} 
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation}
where $\mathcal{M}$ is the stellar mass of the galaxy.
If the target galaxy SFR and stellar mass place the galaxy above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

\begin{figure*}
  \begin{center}
    \leavevmode
     \label{fig:smf}
     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}
    \end{center}
\end{figure*}

\subsection{Galaxy Environment} \label{sec:environment}
In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
account for the PRIMUS redshift errors and redshift space distortions.  
Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
 such as the masses of their host dark matter halos.
Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
within the scales of the host dark matter halos.
We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
%include a sentence that sums up everything in Croton and Muldrew?

In order to measure environment using an aperture defined above, we first construct a volume limited 
{\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at each redshift bin. 
The $M_{r}$ cut-offs are selected so that the cumulative number density over $M_{r}$ at all redshift bins are equal. 
By equating the cumulative number densities at different redshifts not only can we reasonably compare the 
environment values at different redshift bins but we also attempt to build an EDP that has a similar galaxy 
population in all of the redshift bins i.e. accounts for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
Furthermore \cite{Behroozi:2013aa} %%%FINISH THIS SENTENCE

To construct the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
target galaxies, described in Section \ref{sec:target}. 
We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. 
Before we consider the cumulative number densities in these bins, we first determine $M_r$ limit for the 
highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ 
and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ 
have fewer galaxies than the bin at $M_{r, \rm{lim}}$. 
We choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be, conservatively, $M_{r} = -20.75$. 
For the other redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such 
that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative 
number density of the highest redshift bin. 
The cumulative number density calculations accounts for the statistical weights of the galaxies (Section 
\ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter SDSS EDP), we do not use the parent data of 
the SDSS-{\em GALEX} target sample the geometry of the combined angular selection function of the 
SDSS VAGC and {\em GALEX}. 
Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
to the entire SDSS VAGC to include galaxies outside of the {\em GALEX} window function. 
Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
$z \sim 0.01$ in the SDSS VAGC data.  
The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
by the faint limit of the $M_{r}$ versus redshift distribution. 
The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
a function of redshift for the EDP (red) and the target galaxy sample (black).
